---
title: "Step 4 : Compare IC50"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a04-compare-IC50}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, 
  warning = FALSE
)
library(magrittr)
library(flextable)
```

```{r setup}
library(batchCurve)
```



## Naming format

A typical use case for IC50 comparisons is a collection of IC50 estimates for a mutant cell vs the parent wild type. batchCurve relies on a naming format to determine the mutant-parent identities:

* **parent_gene_variant**

For each compound-mutant combination, the tool will compare to a matching  compound-parent based on the first text components in the ID. For example, highlighted in blue are appropriate parent names that will allow for comparison to <span style="color: blue;">**Dd2**</span>_ProtB5-M45I (red will not):

* <span style="color: blue;">**Dd2**</span>
* <span style="color: blue;">**Dd2-A**</span>
* <span style="color: red;">**Dd2_A**</span>
* <span style="color: red;">**3D7**</span>


## Example

batchCurve comes bundled with a number of example dose-response sample files: The example file ("compare_results.csv") contains multiple repeat assays for a number of compound-mutant combinations.

```{r}
# lists the names of available example data files
batchCurve_example()
```

Here we run compare and show a shortened view of the output file.
```{r}
# example file contains mutltiple repeat assays for a number of compound-mutant combinations
d <- utils::read.csv(batchCurve_example(file = "compare_results.csv"))
cp <- compare(data = d, prefix = 'example')

cp[,c(1:2,4:6,12, 14)] %>% head(3) %>%
  flextable::flextable() 
```

The plotting function returns a list of plots as well as a pdf export file.

```{r , message=FALSE, warning=FALSE, fig.width=5, fig.asp= 0.9, dpi= 300, out.width=450, out.height=350, fig.align='center'}
knitr::opts_chunk$set(dev = 'pdf')
p <- head(cp, 3) %>% plot_mean(prefix = 'example')
p[1]
```

